---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coconut

<!-- badges: start -->
<!-- badges: end -->


The coconut packages allows you to animate text in Rmd documents (xaringan slides included) and Shiny apps using the [Animate.css](https://animate.style/) library. 


## Installation

You can install the development version of coconut from Github with:


```{r, eval=FALSE}

install.packages("remotes")

remotes::install_github("feddelegrand7/coconut")

```

## How to use it ? 

Put the `use_coco()` function at the beginning of your Rmd document (works also with xaringan slides) or Shiny application (at the UI): 

```{r}

library(coconut)

use_coco()

```

Then you can animate your text using the `coconut()` function. Don't hesitate to use `help("cocunut")` to check out additional arguments.

> The Github README doesn't allow for animation but it should work on your RMarkdown document or Shiny app. 




```{r}

coconut(text = "What comes first: filter or select ?!!!", level = "###", animation = "bounce")


```


For a listing of all the available animations provided by the __Animate.css__ library, use the following function: 


```{r}

available_animations()


```


# Example 

This is an example of a Shiny app that uses `coconut`


```{r, eval=FALSE}

library(shiny)
library(coconut)

ui <- fluidPage(use_coco(), 
                
                
  coconut(text = "HELLO SHINY !!!!", level = "#", animation = "backInDown", duration = "slower")
            

)

server <- function(input, output) {


}

shinyApp(ui = ui, server = server)


```





















